Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline

### 2017-05-11 Ben_Manuscripts/Outlines/Paper1_Outline.tex
Outline edits

	Nanostructured membranes can bypass many of the performance issues which plague traditional NF and RO membranes.
	\begin{itemize}
		\item With nanostructured materials, solute rejecting pores can be tuned uniformly -- drives down energy requirements
		\item Targeted separations can be accomplished by tuning the molecular building blocks which form these materials
		\item Entirely different mechanisms govern the separation processes in various nanostructured materials which can inspire novel separation techniques
	\end{itemize}

@@

	A molecular level understanding of LLC membrane structure will elucidate small molecule transport mechanisms, providing guidelines to reduce the chemical space for design of monomers used to create separation-specific membranes.
	\begin{itemize}
                \item We do not yet understand how to reduce the effective pore size and/or tune the chemical environment in the HII nanopores for effective water desalination and small organic separations. Rejection studies show that this membrane can not do desalination yet
%MRS: ^^^nice way to turn a weakness of the materials class into an opportunity to improve them requring research! 
		\item Colh phase studies currently limited to one monomer
                \item Optimization efforts performed through trial and error over the past 20 years
                \item Macroscopic models are the only source of predictive modeling and existing theories do not adequately describe transport at these length scales
                \begin{itemize}
                        \item What does the microscopic pore structure look like?
			\item Do ions have trouble getting through because of interactions with other things in the pores (e.g. ions, carbonyl groups, benzene rings) -- related to ionic conduction
%MRS2: ``related to ionic conduction'' is vague
			\item Is rejection of ions due to Donnan exclusion?
                        \item Do neutral solutes get rejected based solely on size rejection, or do interactions within the pore lead to selective rejection?
                        \item Is water structured inside the pores, restricting low energy pathways for solutes to follow? 
%BJC: saw something like this in a paper 
%MRS2: good, cite if you can.
		\end{itemize}
		\item How can microscopic pore structure guide membrane design?
                  \begin{itemize}
		\item An atomistic understanding of the mechanism of solute transport can identify performance bottle necks and direct design of future monomers/membranes
		\item We can use molecular dynamics simulations to enhance our understanding 
                  \end{itemize}
	\end{itemize}

	A clear picture of the nanoscopic structure of LLC membranes, gained by building 
%MRS2: suggest ``molecular models'', as one can argue that each way of doing it is a different model, or that it might require trying 2-3 things.
a molecular model, will provide evidence to support or call into question past drawn conclusions that have largely guided our understanding of separation mechanisms. 
	\begin{itemize}
%MRS2: a thought - it would be great to add what is exactly meant by ``pore walls'' and how well defined they are is not clear. For example, how strict is the division between the hydrophobic tails, the head groups, and the ionic groups?  This directly affects what is meant by the ``size'' of the nanopore, and (to put somewhere else in the outline) what size exclusion means.
 		\item The arrangement of sodium ions in the channels is thought to be confined to the pore walls. It is possible they are arranged more randomly
		\begin{itemize}
			\item This could change how one thinks about molecules diffusing through membrane
			\item Could also be a difference between lyotropic and thermotropic phases
		\end{itemize}
		\item The Colh phase is described as having pores made of disks or layers stacked on top of one another, each containing a set number of monomers. 
		\begin{itemize}
			\item How do the monomer head groups pack together? Do the benzene rings prefer to be stacked on top of each other or in another pi-stacking mode.
			\item Gas phase ab initio studies of benzene dimers have shown a clear energetic advantage for a parallel displaced or T-shaped conformation versus a stacked conformation. 
			\item Substituted benzene rings exhibit an even stronger pi-stacking attraction %BJC: reference ab initio papers   	
			\item A simple simulation study of a similar molecule (Head group is a sulfonate in the meta position) suggests that there are 4 monomers in each disk
			\item Calculations based on the volume of the liquid crystal suggest that there are seven monomers in each layer % reference 2005-ish Zhou paper 
		\end{itemize}
		\item It is possible there is more than one metastable states associated with this LLC system
		\begin{itemize}
			\item Which phase is consistent with experiment?
			\item Can both phases be created experimentally?
			\item How will each state affect transport?
		\end{itemize}
	\end{itemize}

@@

	%BJC: I'm not sure where to place this figure. ACS nano requires the methods section to go last (after conclusions). It seems like this should go earlier, but it fits the context best around here.
	\begin{figure}
	\centering
	\begin{subfigure}{.45\linewidth}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{}\label{fig:chemdraw}
	\end{subfigure}
	\begin{subfigure}{.45\linewidth}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{}\label{fig:monatomistic}
	\end{subfigure}
	\medskip
	\begin{subfigure}{.45\linewidth}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{}\label{fig:cartoonlayer}
	\end{subfigure}
	\begin{subfigure}{.45\linewidth}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{}\label{fig:layeratomistic}
	\end{subfigure}
	\caption{(a) The chemical structure of NAGA3C11 (b) The chemical structure visualized atomistically enhances intuition about system behavior %MRS2: in what way? (c) Wedge-shaped monomers assemble into layers (d) An atomistic view of a layer suggests geometric constraints based on monomer structure %MRS2: suggests what?}\label{fig:cartoonvatomistic}  
	\end{figure}

	The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable length for an atomistic simulation, calling for a more efficient way to build the system. 
	\begin{itemize}
          %MRS2: specify what type of self assembly -- could be that layers are faster than hexagonal pores to get to.
		\item Work done shows coarse grain model self assembly in ~1000 ns , Citation: J. Phys. Chem. B 2013, 117, 4254-4262
		\item Attempts with Colh system not fruitful  
		\begin{itemize}
			\item Packed monomers into box with Packmol
			\item Simulated for ~100 ns with no progress shown towards self assembly
		\end{itemize}  
		\item Wrote code to assemble monomers into Colh configuration close to what is expected 
		\item Equilibration simulations allow structure to relax into expected configuration 
	\end{itemize}

%MRS2: need to be careful describing which stacking/layering is described where/when based on experiments actually reported.
	Each pore is made of twenty stacked monomer layers with periodic continuity in all directions, avoiding any edge effects and creating an infinite length pore ideal for studying transport (Fig.~\ref{fig:initial})
	\begin{itemize}
		\item A thinner system is better to reduce the computational cost and allow us to look at longer timescales
		\item Number of layers chosen to give sufficient resolution when simulating XRD patterns
                \item Decided on 20 layers using a system which held a vacuum gap above and below the membrane
                \item Too few layers leads to micelle-like formations %MRS: with gap.
	\end{itemize}

	\noindent Initial guesses for the remaining structural parameters were chosen based on experimental data and treated as variables during model development 
%MRS2: ``treated as variables'' is vague. Be specific about what it means you are doing.
	\begin{itemize}
		\item XRD gives pore-to-pore distances of $\approx$ 4.1 nm and indicates possible pi-stacking at $\approx$ 3.7 \angstrom (see figure~\ref{fig:xrd}) on - comparison of experimental vs. simulated)
		\item Pi-stacking exists in multiple stable configurations: sandwiched, T-shaped and parallel-displaced
		\item T-shaped and parallel-displaced are nearly isoenergetic and more stable than the sandwiched configuration.
		\item T-shaped configuration is most stable when benzene centers are $\approx$ 5 \angstrom apart which is not consistent with WAXS. % http://www.jbc.org/content/273/25/15458.full 
		\item System made with stacked and parallel-displaced benzene rings to see what is favored and matches XRD
		\item TEM images and rejection studies give a pore size estimate
	\end{itemize}

@@

	Simulated X-ray diffraction patterns were generated based on atomic coordinates to give a deeper understanding of the pore structure and spacing. 
        \begin{itemize}
               \item 3 dimensional Fourier transformed electron density generates simulated 1D and 2D diffraction patterns
               \item The 1D patterns are generated by spherical integration of the FT
               \item 2D patterns are generated by taking cross sections of the FT in the qx, qy and qz planes
               \item We matched experiments based on iterative improvement of our choice in initial structure and equilibration procedure
                 %MRS2: ``iterative improvement'' is vague -- other researchers could not implement that (unless you say you give details elsewhere)
        \end{itemize}

@@

	The initial distance between layers is a key determining factor of the equilibrium configuration.
	\begin{itemize}
                \item In the real system, layers are stacked 3.7 \angstrom apart based on WAXS data. 
                \item A characteristic of all systems simulated in this way, is a defined, cylindrical and open pore structure. Benzene rings arrange in a helical conformation after equil. Membrane about 8 nm thick (Fig ~\ref{fig:phaseA}) % BJC: Still trying to prove that layered is trying to go towards a helical conformation. Also, maybe include thickness in the table?
                \item This will be called phase A for simplicity  
	        \item Simulations of systems built with layers stacked 5 \angstrom apart results in a pore structure characterized by high radial disorder.
%MRS2: higher radial disorder - make clear still hydrophobic/hydrophilic.
        	\begin{itemize}
                	\item This will be called phase B (Fig~\ref{fig:phaseB})
                	\item The arrangement of sodium ions (which are closely bound to carbonyl head groups) can be well-approximated by a gaussian distribution 
                          %MRS2: below: ``Only difference''.  Only difference is in how they are prepared.  But presumably, there are a number of initial configurations that can lead to this one, so emphasizing that it's the only difference isn't that important.  Also, we want to be emphasizing the thermodynamic differences, not kinetics.
                	\item Like phase A, phase B can form at 280K. The only difference in simulations leading to this state, is the initial interlayer spacing
                	\item The phase is also present when phase A is heated close to its isotropic transition point
                	\item There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})
                	\begin{itemize}
                        	\item Phase B has a closed pore, while phase A is open. This will impact transport mechanisms
                        	\item Phase B membranes are thicker
                        	\item Consequently, the pore spacing is smaller
                	\end{itemize}
		\end{itemize}
                \item We have at least two metastable states
        \end{itemize}

	We varied the relative interlayer orientation between sandwiched and parallel-displaced based on our knowledge of the stability of these two pi-stacking modes.
        \begin{itemize}
		\item Simulated Xray diffraction patterns generated from initial configurations of each pi-stacking mode, shows a 
%MRS2: ``clear relation'' is a bit indirect. 
clear relation between the parallel displaced configuration and major features present in the XRD patterns %BJC: A figure would probably be good here %MRS2: yep, refer a figure here.
		\item Diagonal spots in the alkane chain region are only generated for structures created in the parallel displaced configuration
		\item However, both configurations are stable for 100's of nanoseconds
		\item Xray diffraction of the sandwiched configuration after equilibration shows the spots. This indicates that there is a shift towards the offset configuration.
	\end{itemize}

@@

	\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{placeholder.png}
	\caption{As temperature is increased, Phase A transitions to Phase B, as indicated by the shown order parameter. An order parameter of 1 indicates perfect ordering, while 0 indicates disorder}\label{fig:transition}
%MRS2: maybe provide a bit more information what data will be here?  Order parametr vs time? One panel with order paramter vs. time, one with configurations from 0 and 1 endpoints?
	\end{figure}

	\begin{table}
	\centering
	\begin{tabular}{|c|c|}
	\hline
	table & here \\
	\hline
	\end{tabular}
        %MRS2: what is the thesis here?
	\caption{A system built with 5 monomers per layer in a parallel displaced configuration results in a structure closest to experimental data}\label{table:p2p} 
	\end{table}

	\begin{figure}
	\centering
	\begin{subfigure}{.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{~\label{fig:phaseA}}
	\end{subfigure}
	\begin{subfigure}{.45\textwidth}
		\includegraphics[width=\linewidth]{placeholder.png}
		\centering
		\caption{~\label{fig:phaseB}}
	\end{subfigure}
	\caption{There are clear differences in pore structure between systems built with layers stacked (a) 3.7 \angstrom apart and (b) 5.0 \angstrom apart}
        %MRS2: explain theses?  Also, the exact configurations used to start them are probably not that important; many different initial configurations will probably lead to most of them.  It's the thermodyamics that are important.
	\label{fig:porestructures}
	\end{figure}

	%BJC: I might eliminate the other paragraph (2 before this one), where I justify parallel-displaced vs. sandwiched, and do it all in this paragraph.	
        %MRS2: a little hard to say until the data is in.
	Full comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration made up of 5 monomers per layer.
	\begin{itemize}
		\item Phase A
		\begin{itemize}	
			\item Purely stacked configuration is missing reflections at 2, 4, 8 and 10 0'clock, but they are there in the parallel displaced conformation
			\item There is evidence that the stacked configuration will shift towards an offset configuration over time. WAXS spots show up after short simulations, in which case there is visible movement away from a perfectly stacked, towards a parallel displaced conformation 
			\item Pi-stacking reflections are present in all cases but at spacings higher than shown experimentally. This is not surprising since GAFF will not properly treat pi-stacking.
			\item Interestingly, the spots, which are usually associated with alkyl chain tilt, still appear with an average tilt angle of 0 degrees
		\end{itemize}
		\item Phase B
		\begin{itemize}
			\item Stacking refelctions present indicating separation of $\approx$ 5 \angstrom
			\item No spots at all which is consistent with the disorder shown by the rings in the pore
		\end{itemize}
		\item Both phases show a ring in the simulated 2D WAXS patterns at q $\approx$ 1.4 \angstrom\textsuperscript{-1} which is typical of packed alkane chains
		\item Both phases exhibit axial reflections. Even though the rings are not ordered in phase B, 
%MRS2: not quite clear what physical structures the axial reflections correspond to (what are the distances? What do they correspond to?)
they are still partitioned into layers which gives rise to an axial refelction at the same distance where we expect alkane chain packing to be present   
%MRS2: how are they layers defined here? Can you bring in more information about the nonuniformity of the density?
	\end{itemize}

	\begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{~\label{fig:xrdA}}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{~\label{fig:xrdexp}}
	\end{subfigure}
        \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\linewidth]{placeholder.png}
                \caption{~\label{fig:xrdB}}
        \end{subfigure}
	\caption{Phase A (a) provides a good match to experiment (b). Phase B (c) is missing reflections present in the experimental pattern} % BJC: any more detail?  %MRS2: yes, give distances, and describe what you mean as ``good match''
	\label{fig:xrd}
	\end{figure}

@@

	\begin{table}
	\centering
	\begin{tabular}{|c|c|}
	\hline
	Nernst Einstein & Collective Diffusion \\
	\hline
	\end{tabular}
	\caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion agree within error. Both methods give calculated values of ionic conductivity which are higher than experimental values~\label{table:conductivity}}
%MRS2: I would say that they are reasonable close to experiment, though higher. Also somewhat contradicted in other places.
	\end{table}

@@

	\section{Supplemental Information} %MRS2: check, might be called supporting information, depending on the journal.

@@

>>>>

	Nanostructured membranes can bypass many of the performance issues which plague traditional NF and RdO membranes.
	\begin{itemize}
		\item With nanostructured materials, solute rejecting pores can be tuned uniformly -- drives down energy requirements
		\item Targeted separations can be accomplished by tuning the molecular building blocks which form these materials
		\item Entirely different mechanisms govern the separation processes in various nanostructured materials which can inspire novel separation techniques
	\end{itemize}

@@

	A molecular level understanding of LLC membrane structure will elucidate small molecule transport mechanisms, providing guidelines to reduce the chemical space for design of monomers used to create separation-specific membranes.
	\begin{itemize}
                \item We do not yet understand how to reduce the effective pore size and/or tune the chemical environment in the HII nanopores for effective water desalination and small organic separations. Rejection studies show that this membrane can not do desalination yet
%MRS: ^^^nice way to turn a weakness of the materials class into an opportunity to improve them requring research! 
		\item Colh phase studies currently limited to one monomer
                \item Optimization efforts performed through trial and error over the past 20 years
                \item Macroscopic models are the only source of predictive modeling and existing theories do not adequately describe transport at these length scales
                \begin{itemize}
                        \item What does the microscopic pore structure look like?
			\item Do ions have trouble getting through because of interactions with other things in the pores (e.g. ions, carbonyl groups, benzene rings) -- related to ionic conduction
			\item Is rejection of ions due to Donnan exclusion?
                        \item Do neutral solutes get rejected based solely on size rejection, or do interactions within the pore lead to selective rejection?
                        \item Is water structured inside the pores, restricting low energy pathways for solutes to follow? 
%BJC: saw something like this in a paper 
%MRS2: good, cite if you can.
		\end{itemize}
		\item How can microscopic pore structure guide membrane design?
                  \begin{itemize}
		\item An atomistic understanding of the mechanism of solute transport can identify performance bottle necks and direct design of future monomers/membranes
		\item We can use molecular dynamics simulations to enhance our understanding 
                  \end{itemize}
	\end{itemize}

	A clear picture of the nanoscopic structure of LLC membranes, gained by building 
%MRS2: suggest ``molecular models'', as one can argue that each way of doing it is a different model, or that it might require trying 2-3 things.
molecular models, will provide evidence to support or call into question past drawn conclusions that have largely guided our understanding of separation mechanisms. 
	\begin{itemize}
%MRS2: a thought - it would be great to add what is exactly meant by ``pore walls'' and how well defined they are is not clear. For example, how strict is the division between the hydrophobic tails, the head groups, and the ionic groups?  This directly affects what is meant by the ``size'' of the nanopore, and (to put somewhere else in the outline) what size exclusion means.
 		\item The arrangement of sodium ions in the channels is thought to be confined to the pore walls. It is possible they are arranged more randomly
		\begin{itemize}
			\item This could change how one thinks about molecules diffusing through membrane
			\item Could also be a difference between lyotropic and thermotropic phases
		\end{itemize}
		\item The Colh phase is described as having pores made of disks or layers stacked on top of one another, each containing a set number of monomers. 
		\begin{itemize}
			\item How do the monomer head groups pack together? Do the benzene rings prefer to be stacked on top of each other or in another pi-stacking mode.
			\item Gas phase ab initio studies of benzene dimers have shown a clear energetic advantage for a parallel displaced or T-shaped conformation versus a stacked conformation. 
			\item Substituted benzene rings exhibit an even stronger pi-stacking attraction %BJC: reference ab initio papers   	
			\item A simple simulation study of a similar molecule (Head group is a sulfonate in the meta position) suggests that there are 4 monomers in each disk
			\item Calculations based on the volume of the liquid crystal suggest that there are seven monomers in each layer % reference 2005-ish Zhou paper 
		\end{itemize}
		\item It is possible there is more than one metastable states associated with this LLC system
		\begin{itemize}
			\item Which phase is consistent with experiment?
			\item Can both phases be created experimentally?
			\item How will each state affect transport?
		\end{itemize}
	\end{itemize}

@@

	%BJC: I'm not sure where to place this figure. ACS nano requires the methods section to go last (after conclusions). It seems like this should go earlier, but it fits the context best around here.
	%BJC2: I think I might make this a six panel figure. The other two panels will show a cartoon and atomistic pore view.
	\begin{figure}
	\centering
	\begin{subfigure}{.45\linewidth}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{}\label{fig:chemdraw}
	\end{subfigure}
	\begin{subfigure}{.45\linewidth}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{}\label{fig:monatomistic}
	\end{subfigure}
	\medskip
	\begin{subfigure}{.45\linewidth}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{}\label{fig:cartoonlayer}
	\end{subfigure}
	\begin{subfigure}{.45\linewidth}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{}\label{fig:layeratomistic}
	\end{subfigure}
	\caption{(a) The chemical structure of NAGA3C11 (b) The chemical structure visualized atomistically enhances intuition how monomers might pack together %MRS2: in what way?
(c) Wedge-shaped monomers assemble into layers (d) An atomistic view of a layer suggests a reasonable range of monomers per layer to test\label{fig:cartoonvatomistic}  
	\end{figure}

	The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable length for an atomistic simulation, calling for a more efficient way to build the system. 
	\begin{itemize}
          %MRS2: specify what type of self assembly -- could be that layers are faster than hexagonal pores to get to.
	  %BJC2: Don't I suggest the type of self assembly to be assembly into the hexagonal phase? Or should I be more broad as in, we see no type of self-assembly occuring.
		\item Work done shows coarse grain model self assembly in ~1000 ns , Citation: J. Phys. Chem. B 2013, 117, 4254-4262
		\item Attempts with Colh system not fruitful  
		\begin{itemize}
			\item Packed monomers into box with Packmol
			\item Simulated for ~100 ns with no progress shown towards self assembly
		\end{itemize}  
		\item Wrote code to assemble monomers into Colh configuration close to what is expected 
		\item Equilibration simulations allow structure to relax into expected configuration 
	\end{itemize}

%MRS2: need to be careful describing which stacking/layering is described where/when based on experiments actually reported.
%BJC2: can you clarify this point?
	Each pore is made of twenty stacked monomer layers with periodic continuity in all directions, avoiding any edge effects and creating an infinite length pore ideal for studying transport (Fig.~\ref{fig:initial})
	\begin{itemize}
		\item A thinner system is better to reduce the computational cost and allow us to look at longer timescales
		\item Number of layers chosen to give sufficient resolution when simulating XRD patterns
                \item Decided on 20 layers using a system which held a vacuum gap above and below the membrane
                \item Too few layers leads to micelle-like formations %MRS: with gap.
	\end{itemize}

	\noindent Initial guesses for the remaining structural parameters were chosen based on experimental data and varied in order to develop a model that agrees with experiment. 
%MRS2: ``treated as variables'' is vague. Be specific about what it means you are doing.
	\begin{itemize}
		\item XRD gives pore-to-pore distances of $\approx$ 4.1 nm and indicates possible pi-stacking at $\approx$ 3.7 \angstrom (see figure~\ref{fig:xrd}) on - comparison of experimental vs. simulated)
		\item Pi-stacking exists in multiple stable configurations: sandwiched, T-shaped and parallel-displaced
		\item T-shaped and parallel-displaced are nearly isoenergetic and more stable than the sandwiched configuration.
		\item T-shaped configuration is most stable when benzene centers are $\approx$ 5 \angstrom apart which is not consistent with WAXS. % http://www.jbc.org/content/273/25/15458.full 
		\item System made with stacked and parallel-displaced benzene rings to see what is favored and matches XRD
		\item TEM images and rejection studies give a pore size estimate
	\end{itemize}

@@

	Simulated X-ray diffraction patterns were generated based on atomic coordinates to give a deeper understanding of the pore structure and spacing. 
        \begin{itemize}
               \item 3 dimensional Fourier transformed electron density generates simulated 1D and 2D diffraction patterns
               \item The 1D patterns are generated by spherical integration of the FT
               \item 2D patterns are generated by taking cross sections of the FT in the qx, qy and qz planes
               \item We matched experiment by varying the initial structure. The selection of initial structure is explained later
        \end{itemize}

@@

	The initial distance between layers is a key determining factor of the equilibrium configuration.
	\begin{itemize}
                \item In the real system, layers are stacked 3.7 \angstrom apart based on WAXS data. 
                \item A characteristic of all systems simulated in this way, is a defined, cylindrical and open pore structure. Benzene rings arrange in a helical conformation after equil. Membrane about 8 nm thick (Fig ~\ref{fig:phaseA}) % BJC: Still trying to prove that layered is trying to go towards a helical conformation. Also, maybe include thickness in the table?
                \item This will be called phase A for simplicity  
	        \item Simulations of systems built with layers stacked 5 \angstrom apart results in a pore structure characterized by high radial disorder, while maintaining partitioning between hydrophobic and hydrophilic regions.
        	\begin{itemize}
                	\item This will be called phase B (Fig~\ref{fig:phaseB})
                	\item The arrangement of sodium ions (which are closely bound to carbonyl head groups) can be well-approximated by a gaussian distribution 
                          %MRS2: below: ``Only difference''.  Only difference is in how they are prepared.  But presumably, there are a number of initial configurations that can lead to this one, so emphasizing that it's the only difference isn't that important.  Also, we want to be emphasizing the thermodynamic differences, not kinetics.
                	\item Like phase A, phase B can form at 280K. %BJC2: ^^ so get rid of this part : The only difference in simulations leading to this state, is the initial interlayer spacing
                	\item The phase is also present when phase A is heated close to its isotropic transition point
                	\item There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})
                	\begin{itemize}
                        	\item Phase B has a closed pore, while phase A is open. This will impact transport mechanisms
                        	\item Phase B membranes are thicker
                        	\item Consequently, the pore spacing is smaller
                	\end{itemize}
		\end{itemize}
                \item We have at least two metastable states
        \end{itemize}

	We varied the relative interlayer orientation between sandwiched and parallel-displaced based on our knowledge of the stability of these two pi-stacking modes.
        \begin{itemize}
		\item Simulated Xray diffraction patterns generated from initial configurations of each pi-stacking mode, shows a 
%MRS2: ``clear relation'' is a bit indirect. 
%BJC2: clear link? 
clear link between the parallel displaced configuration and major features present in the XRD patterns %BJC: A figure would probably be good here %MRS2: yep, refer a figure here.
		\item Diagonal spots in the alkane chain region are only generated for structures created in the parallel displaced configuration
		\item However, both configurations are stable for 100's of nanoseconds
		\item Xray diffraction of the sandwiched configuration after equilibration shows the spots. This indicates that there is a shift towards the offset configuration.
	\end{itemize}

@@

	\begin{figure}
	\centering
	\begin{subfigure}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{}\label{fig:orderparameter}
	\end{subfigure}
	\begin{subfigure}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{}\label{fig:order}
	\end{subfigure}
	\begin{subfigure}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{}\label{fig:disorder}
	\end{subfigure}
	\caption{(a) As temperature is increased, Phase A transitions to Phase B, becoming more disordered. An order parameter of 1 indicates perfect ordering, while 0 indicates disorder. (b) The system is ordered, characteristic of Phase A, initially (c) The system becomes disordered, characteristic of Phase B, as temperature is raised beyond 310K}\label{fig:transition}
%MRS2: maybe provide a bit more information what data will be here?  Order parametr vs time? One panel with order paramter vs. time, one with configurations from 0 and 1 endpoints?
	\end{figure}

	\begin{table}
	\centering
	\begin{tabular}{|c|c|}
	\hline
	table & here \\
	\hline
	\end{tabular}
	\caption{The pore spacing of the model increases as number of monomers in each layer increases. The pore spacing of a system starting in the sandwiched configuration is systematically lower than that started in an offset configuration. Systems built with 5 monomers per layer in a parallel displaced configuration results in a pore spacing closest to experimental data}\label{table:p2p} 
	\end{table}

	\begin{figure}
	\centering
	\begin{subfigure}{.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{~\label{fig:phaseA}}
	\end{subfigure}
	\begin{subfigure}{.45\textwidth}
		\includegraphics[width=\linewidth]{placeholder.png}
		\centering
		\caption{~\label{fig:phaseB}}
	\end{subfigure}
	\caption{There are clear differences in pore structure between systems built with layers stacked (a) 3.7 \angstrom apart and (b) 5.0 \angstrom apart}
        %MRS2: explain theses?  Also, the exact configurations used to start them are probably not that important; many different initial configurations will probably lead to most of them.  It's the thermodyamics that are important.
	%BJC: okay, so just rephrase it, worded in a way that doesn't reference the initial configuration/layer spacing?
	%BJC: what do you  mean by 'thermodynamics that are important' -- just distinguishing which state is more favorable under what conditions?
	\label{fig:porestructures}
	\end{figure}

	%BJC: I might eliminate the other paragraph (2 before this one), where I justify parallel-displaced vs. sandwiched, and do it all in this paragraph.	
        %MRS2: a little hard to say until the data is in.
	Full comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration made up of 5 monomers per layer.
	\begin{itemize}
		\item Phase A
		\begin{itemize}	
			\item Purely stacked configuration is missing reflections at 2, 4, 8 and 10 0'clock, but they are there in the parallel displaced conformation
			\item There is evidence that the stacked configuration will shift towards an offset configuration over time. WAXS spots show up after short simulations, in which case there is visible movement away from a perfectly stacked, towards a parallel displaced conformation 
			\item Pi-stacking reflections are present in all cases but at spacings higher than shown experimentally. This is not surprising since GAFF will not properly treat pi-stacking.
			\item Interestingly, the spots, which are usually associated with alkyl chain tilt, still appear with an average tilt angle of 0 degrees
		\end{itemize}
		\item Phase B
		\begin{itemize}
			\item Stacking refelctions present indicating separation of $\approx$ 5 \angstrom
			\item No spots at all which is consistent with the disorder shown by the rings in the pore
		\end{itemize}
		\item Both phases show a ring in the simulated 2D WAXS patterns at q $\approx$ 1.4 \angstrom\textsuperscript{-1} which is typical of packed alkane chains
		\item Both phases exhibit axial reflections. Even though the rings are not ordered in phase B, 
%MRS2: not quite clear what physical structures the axial reflections correspond to (what are the distances? What do they correspond to?)
they are still partitioned into layers which gives rise to an axial refelction at the same distance where we expect alkane chain packing to be present   
%MRS2: how are they layers defined here? Can you bring in more information about the nonuniformity of the density?
%BJC2: Are you thinking about the fourier transforms? I could bring that in
	\end{itemize}

	\begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{~\label{fig:xrdA}}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{~\label{fig:xrdexp}}
	\end{subfigure}
        \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\linewidth]{placeholder.png}
                \caption{~\label{fig:xrdB}}
        \end{subfigure}
	\caption{Phase A (a) provides a good match to experiment (b). Phase B (c) is missing reflections present in the experimental pattern} % BJC: any more detail?  %MRS2: yes, give distances, and describe what you mean as ``good match''
%BJC2: what is a clear way to describe the spots in the ring. Diagonal reflections? radial spots?
	\label{fig:xrd}
	\end{figure}

@@

	\begin{table}
	\centering
	\begin{tabular}{|c|c|}
	\hline
	Nernst Einstein & Collective Diffusion \\
	\hline
	\end{tabular}
	\caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion agree within error. Both methods give calculated values of ionic conductivity which are higher, but reasonably close to experimental values~\label{table:conductivity}}
%MRS2: I would say that they are reasonable close to experiment, though higher. Also somewhat contradicted in other places.
	\end{table}

@@

	\section{Supplemental Information} %MRS2: check, might be called supporting information, depending on the journal. %BJC2: Also, it's a separate document in ACS nano at least

@@

	Equilibration procedure
